Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

In Figure \ref{fig:valley_intensity} we quantify how the intensity at
the line's center (i.e. the valley) changes with the viewing angle,
the outflow velocity and the optical depth.
These results correspond to a fixed rotational velocity of
\vrot$=100\ \kms$.
The triangles correspond to the RT simulations and the line represents
the DS results. 
The valley intensity is expresed as a fraction of the maximum peak
intensty in the line, as such the valley/peak ratio is always less
than one. 
In every panel we see that the valley/peak ratio decreases as the
observer moves from a line  of sight perpendicular to the rotation
axis onto a parallel line of sight. 
This is a clear demonstration of the viewing angle dependency
introduced by rotation.

>>>>

In Figure \ref{fig:valley_intensity} we quantify how the intensity at
the line's center (i.e. the valley) changes with the viewing angle,
the outflow velocity and the optical depth.
These results correspond to a fixed rotational velocity of
\vrot$=100\ \kms$.
The triangles correspond to the RT simulations and the line represents
the DS results. 
The valley intensity is expresed as a fraction of the maximum peak
intensty in the line, as such the valley/peak ratio is always less
than one. 
In every panel we see that the valley/peak ratio decreases as the
observer moves from a line  of sight perpendicular to the rotation
axis onto a parallel line of sight. 
This is a clear demonstration of the viewing angle dependency
introduced by rotation.
The valley/peak ratio at $\cos\theta=1$ matches results
without rotation, this shows that for increasing rotational velocity
the valley/peak ratio increases.
In turn, for increasing optical depth or outflowing velocity this
ratio decreases.
Again, the DS results correctly follow the trends for the full RT
simulations.
